Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
Rewrite

In this section we show that the classic \emph{rent-or-buy} approach yields an optimal algorithm for $k=3$.
Upon receiving $\alpha$ requests between a pair of nodes, we collocate them in one server until the end of an epoch (that we define precisely later).
To this end, we maintain \emph{components of nodes}, in similar way to \cite{repartition-disc}.

We define the algorithm \TAlg{} in the following way.
\TAlg{} maintains components for each node.
Intially, each node is in its own singleton component.
For each pair of nodes \TAlg{} maintains a counter, initiated $0$, and upon receiving a request to this pair while its nodes are located on different servers, it increases the counter by $1$.
If a counter for a pair $(u,v)$ reaches $\alpha$, \TAlg{} merges the components of $u$ and $v$, and moves to the closest partition, where it each component has all of its nodes in one server.
If no such partition exists, \TAlg{} resets all components to singletons and all counters to $0$ and ends the phase.

@@

  Now we consider the last, unfinished phase.
  Consider the case, where the unfinished phase is also the first one.
  Then, we cannot charge $\OPT$ due to unability to partiton the components.
  Instead, we use the fact that \TAlg and $\OPT$ started with the same initial configuration.
  We charge $\OPT$ $\alpha$ for the first external $\alpha$ requests or a migration,
  and we follow the analysis regarding the unsaturated requests.
  If the input finished before first $\alpha$ external requests, then \TAlg is optimal.

>>>>

In this section we show that the classic \emph{rent-or-buy} approach\cite{borodin-book} allows to obtain an optimal algorithm for $k=3$.
Upon receiving $\alpha$ requests between a pair of nodes, we collocate them in one server until the end of an epoch (that we define precisely later).
To this end, we maintain \emph{components of nodes}, in similar fashion to previous approaches\cite{repartition-disc}.

We say that the request $(u,v)$ is \emph{external}, if the algorithm that receives this request is in the configuration, where $u$ and $v$ are located at different servers.

We define the algorithm \TAlg in the following way.
\TAlg maintains components for each node.
Intially, each node is in its own singleton component.
For each pair of nodes \TAlg maintains a counter, initiated $0$. 
Upon receiving an external request to a pair, it increases the counter by $1$.
If the counter for a pair $(u,v)$ reaches $\alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest partition, in which each component has all of its nodes collocated in one server.
If no such partition exists, \TAlg resets all components to singletons and all counters to $0$ and ends the phase.

@@

  Now we consider the last, unfinished phase.
  Consider the case, where the unfinished phase is also the first one.
  Then, we cannot charge $\OPT$ due to unability to partition the components.
  Instead, we use the fact that \TAlg and $\OPT$ started with the same initial configuration.
  We charge $\OPT$ $\alpha$ for the first external $\alpha$ requests or a migration,
  and we follow the analysis regarding the unsaturated requests.
  If the input finished before first $\alpha$ external requests, then \TAlg is optimal.
